cardinalR: Generating interesting high-dimensional data structures

### 2025-04-26 paper-cardinalR.Rmd
Updated table 2

```{r}
datasets_tb <- tibble(dt = c("mobius_clust_data", 
                             "mobius_clust_tsne_param1", 
                             "mobius_clust_tsne_param2",
                             "mobius_clust_tsne_param3",
                             "mobius_clust_umap_param1",
                             "mobius_clust_umap_param2",
                             "mobius_clust_umap_param3"), 
                      text = c("",
                               "", 
                               "",
                               "",
                               "",
                               "", 
                               ""))
```

>>>>

```{r}
datasets_tb <- tibble(dt = c("mobiusgau", 
                             "mobiusgau_tsne1", 
                             "mobiusgau_tsne2",
                             "mobiusgau_tsne3",
                             "mobiusgau_umap1",
                             "mobiusgau_umap2",
                             "mobiusgau_umap3"), 
                      text = c("Simulated data with a Mobius and a Gaussian in 4-D space.",
                               "The tSNE embedding with perplexity $15$ for mobiusgau.", 
                               "The tSNE embedding with perplexity $30$ for mobiusgau.",
                               "The tSNE embedding with perplexity $5$ for mobiusgau.",
                               "The UMAP embedding with number of neighbors $15$ and minimum distance $0.1$ for mobiusgau.",
                               "The UMAP embedding with number of neighbors $30$ and minimum distance $0.08$ for mobiusgau.", 
                               "The UMAP embedding with number of neighbors $5$ and minimum distance $0.9$ for mobiusgau."))
```
